Robust background subtraction in traffic environments

### 2019-02-12 paper/Paper.tex
paragraphs + distance in pbas description

@@

$F = 1$ implies foreground. The decision involves two parameters: (1) The distance threshold $R(x_i)$,which is defined for each pixel separately and which can change dynamically; and (2) the minimum number $K$, which is a fixed global parameter.\newline

@@

Updating means that for a certain index $k \in \{1...N \}$(chosen uniformly at random), the corresponding background model

@@

the background model. This update, however, is only performed with probability $p = 1/T(x_i)$.Otherwise no update

@@

Is also update (with probability $p = 1/T(x_i)$) a randomly chosen neighboring pixel $y i \in N(x_i)$. Thus, the
background model $B_k(y_i)$ at this neighboring pixel is replaced by its current pixel value $V(y_i)$. \newline
To change the decision treshold $R(x_i)$ is saved an array of recently observed pixel values in the background model $B(x_i)$, we also create an array $\mathbf{D}(x_i) = \{D_1(x_i ),...,D_N(x_i)\}$ of minimal decision distances. Whenever an update of $B_k(x_i)$ is carried out, the currently observed minimal distance $d_{min}(x_i) = min_k dist(I(x_i), B_k(x_i))$ is written to this array: $D_k(x_i) \leftarrow d_{min}(x_i)$. Thus, a history of minimal decision distances is created. The average of these values $\overline{d}_{min}(x_i) = \frac{1}{N} \sum_k D_k(x_i)$ is a measure of the background dynamics. Thanks to that

@@

\newline

@@

>>>>

\begin{equation} \label{eq:F}

@@

$F = 1$ implies foreground. The decision involves two parameters: the distance threshold $R(x_i)$,which is defined for each pixel separately and which can change dynamically; and the minimum number $K$, which is a fixed global parameter.
\paragraph{Update B}

@@

Updating means that for a certain index $k \in \{1...N \}$ (chosen uniformly at random), the corresponding background model

@@

the background model. This update, however, is only performed with probability $p = 1/T(x_i)$. Otherwise no update

@@

It is also updated (with probability $p = 1/T(x_i)$) a randomly chosen neighboring pixel $y_i \in N(x_i)$. Thus, the
background model $B_k(y_i)$ at this neighboring pixel is replaced by its current pixel value $V(y_i)$.
\paragraph{Update R}
To change the decision treshold $R(x_i)$ is saved an array of recently observed pixel values in the background model $B(x_i)$, we also create an array $\mathbf{D}(x_i) = \{D_1(x_i ),...,D_N(x_i)\}$ of minimal decision distances. Whenever an update of $B_k(x_i)$ is carried out, the currently observed minimal distance:
\[ d_{min}(x_i) = min_k dist(I(x_i), B_k(x_i)) \] is written to this array: $D_k(x_i) \leftarrow d_{min}(x_i)$. Thus, a history of minimal decision distances is created. The average of these values $\overline{d}_{min}(x_i) = \frac{1}{N} \sum_k D_k(x_i)$ is a measure of the background dynamics. Thanks to that

@@

\paragraph{Update T}

@@

\paragraph{Distance computation}
The quantity $ dist(I(x_i),B_k(x_i)) $ is computed as:
\frac{\alpha}{\overline{I^m}}|I^m(x_i) - B_k^m(x_i)| + |I^v(x_i) - B_k^v(x_i)|
where $m$ indicates the gradient magnitude and $v$ the pixel intensity value. $\overline{I_m}$ is the average gradient magnitude over the last observed frame. Thus, the fraction $\frac{\alpha}{\overline{I^m}}$ weighs the importance
of pixel values against the gradient magnitude
